Can we distinguish between the speed and scope of acute glucocorticoid responses?

### 2021-01-27 3_r_scripts/1_markdown_document.Rmd
Made a bunch of changes to the algorithm.

@@

@@

>>>>

This is a concept figure of what the simulation is doing:

![](concept.png)\

@@

## Variation in speed but not max

Here is another illustration showing what happens if there is no variation in maximal cort coupled with different amounts of variation in speed (A -> C = adding more variation). In some cases (panel A), apparent variation in max at 30 minutes is really just measuring speed (but at least measuring it well). In others (Panel C), variation in 'max' at 30 minutes just isn't measuring anything, but still looks like there is individual variation.

![](var_in_speed_only.png)\

# Extensions

Leaving notes here for myself. I think that I can pretty easily add:

- Calculate and output area under the curve as a default based on whatever sampling points are chosen. This wouldn't be an additional parameter, but would change as a consequence of the parameters set above.

- Make an extra function that will calculate profile repeatability (Reed & Romero 2019) from a simulated dataset with >1 sample drawn per individual. I *think* I can do this, but looking back quickly at how they actually calculated this, it is kind of a mess that involves counting the number of crossovers between time points. I might still be able to code it that way though, will have to look in more detail.

- Given a set of parameters, could I make the function tell you the optimal times to collect x number of samples if you want to separately estimate speed and scope? Presumably you would want a couple early to get at rapid increase. But if there is very little variation in baseline cort then it might be better not to 'waste' a baseline measure? To really get time to max you kind of need a few samples pre/at/post max right?

@@

- Scenarios to point out:

If there is any variation in speed, observed repeatability in basecort can be entirely attributable to speed even if there is 0 variation in basecort. This situation may be better if there really is a lag between capture and increase, but how do you assess if there is individual variation in the time of that lag?
